---
title: "Ectonometrics 2 CA1b"
author: "Ties van der Veen"
date: "2-2-2020"
output: pdf_document
---

## Rebecca Costello, Ties van der Veen, Matei van der Meer

# I. Preliminaries

```{r message=FALSE, warning=FALSE}
#Clearing the workspace

rm(list=ls())
```

```{r message=FALSE, warning=FALSE}
#Calling packages in library

library(foreign)
library(tidyverse)
library(ggdag)
library(dplyr)
library(tinytex)
library(jtools)
library(huxtable)
library(summarytools)
library(ggstance)
library(pwr)
library(knitr)
library(lemon)
library(AER)
library(lubridate)
library(ggplot2)
library(interflex)
library(plm)
library(margins)
```

```{r message=FALSE, warning=FALSE}
#Improving layout of summarise command

knit_print.data.frame <- lemon_print
```

```{r message=FALSE, warning=FALSE}
#Telling summarytools we're in R markdown

st_options(plain.ascii = FALSE, style = "rmarkdown")
st_css()
```

# II. Introduction to the computer assignment

```{r}
#Obtaining the data

theUrl_ca1b_ectrics2 <- "https://surfdrive.surf.nl/files/index.php/s/aaEVKXoZ3VTUbq3/download"
waste2 <- read.dta (file = theUrl_ca1b_ectrics2)
```

```{r}
#Generating a dichotomous variable from a continuous variable (pre-treatment level of unseperated waste ''sorting'')

high_sorting <- as.numeric(waste2$sorting >= 61)
waste2$high_sorting=high_sorting
waste2$low_sorting=(1-waste2$high_sorting)
```

# III. What to submit

## A. Binary intercation variable

(a)

```{r}
#Regression for the fully interacted model

ate3 <- plm(residual_weight ~ treatment*high_sorting, data=waste2, effect = "twoways",
            model = "within", index = c("route", "week"))
coeftest(ate3, vcov=vcovHC(ate3, cluster= "group"))
```

(b)

High_sorting being 0 would give a CATE of just the treatment variable, so -1.015812.

(c)

High_sorting being 1 would give a CATE of -0.040319

(d)

Yes, if people have low sorting then we expect to see a bigger effect from the treatment than if they already sort well (and thus are high sorting).

(e)

The treatment variable itself is significant, yet the treatment*interaction term coefficient is not. So it seems to be unlikely that this would be statistically significant.

## B. Continuous interaction variable

```{r}
#Re-importing the data to get the continuous variable ''sorting'' back

theUrl_ca1b_ectrics2 <- "https://surfdrive.surf.nl/files/index.php/s/aaEVKXoZ3VTUbq3/download"
waste2 <- read.dta (file = theUrl_ca1b_ectrics2)
```

(f)

```{r}
ate4 <- plm(residual_weight ~ treatment*sorting, data=waste2, effect = "twoways",
            model = "within", index = c("route", "week"))
coeftest(ate4, vcov=vcovHC(ate4, cluster= "group"))
```

(g)

```{r}
# print(-0.0989032(mean(waste2$sorting)*(-0.0156784))) 
# tried this function and it didn't work, not sure why.
```


(h)

The interaction term is significant, showing that the treatment and sorting level have a statistically significant effect together.

(i)

```{r}
out2 <- inter.binning(Y = "residual_weight", D = "treatment", X = "sorting",
                     Z = NULL, FE=c("route", "week"), data=waste2, na.rm=TRUE,
                     vartype="cluster", cl="route", main=NULL,
                     wald=TRUE, ylab="conditional average treatment effect")
out2$graph
```

(j)

The low value bin has a higher CATE than the other two, though the interval has a lot of common area between the three. So the difference is actually not very big.

















